Non-kissing and non-crossing complexes \\ for locally gentle algebras

### 2018-07-11 draft/accordionComplexSurfaces.tex
last figure

%\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
%The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
%\end{theorem}
%
%This result follows from the existence of flips in non-kissing facets.
%This operation is illustrated in \fref{fig:flip}.

@@

\begin{example}
\label{exm:peakDeepFacets}
We have seen in Definition~\ref{def:straightBending} that each vertex~$p$ of~$Q$ gives rise to a \defn{peak walk}~$p_\peak$ (resp.~\defn{deep walk}~$p_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\NKC$.
As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\NCC[\surface_{\bar Q}]$.

For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ on the counterclockwise order around the boundary of~$\surface$.
For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
\begin{itemize}
\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise direction (resp.~clockwise direction).
\end{itemize}
Examples are illustrated in \fref{fig:peakDeep}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{peakDeep}}
	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
	\label{fig:peakDeep}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{flip}}
	\caption{A schematic representation of flips in the non-kissing complex. The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau$ and~$\nu = \rho \sigma \tau'$. The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
	\label{fig:flip}
\end{figure}

@@

\begin{proposition}
\label{prop:mutationAccordions}
Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.  We represent all curves on the universal cover of~$\surface(\bar Q)$.
Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may go to infinity if punctures are involved). 
\begin{itemize}
 \item Exactly one of the curves obtained by changing the~$\SSS$ to a~$\ZZZ$ and conversely by moving the endpoints of~$\gamma$ along the top and bottom curves is a~$\dissection$-accordion.
 \item This~$\dissection$-accordion yields the flip or mutation of~$F$ at~$\gamma$.
 \item If the flip is positive, then the~$\SSS$ is turned into a~$\ZZZ$.  If the flip is negative, then the~$\ZZZ$ is turned in to an~$\SSS$.
\end{itemize}
\end{proposition}
\begin{proof}
 Let~$\omega = \walk(\gamma)$.  Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figure \ref{fig:flip}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.
 \pierreguy{1 picture here.}

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & 0 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{gcdVectors}}
	\caption{A non-kissing facet (left), an accordion facet (middle) and a slalom facet (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}. The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
	\label{fig:gcdVectors}
\end{figure}
\end{example}

>>>>

%\begin{theorem}[{\cite[Cor.~2.27 \& Cor.~2.33]{PaluPilaudPlamondon}}]
%The reduced non-kissing complex~$\RNKC$ is pure of dimension~$|Q_0|$ (\ie all maximal faces have dimension~$|Q_0|$) and thin (\ie all codimension~$1$ faces are contained in exactly two facets).
%\end{theorem}
%
%This result follows from the existence of flips in non-kissing facets.
%This operation is illustrated in \fref{fig:flip1}.

@@

\begin{example}
\label{exm:peakDeepFacets}
We have seen in Definition~\ref{def:straightBending} that each vertex~$p$ of~$Q$ gives rise to a \defn{peak walk}~$p_\peak$ (resp.~\defn{deep walk}~$p_\deep$) with a single peak (resp.~deep) at~$v$ and no other corner.
The set of all such walks forms the \defn{peak facet}~$\set{p_\peak}{p \in Q_0}$ (resp.~the \defn{deep facet}~$\set{p_\deep}{p \in Q_0}$) of the non-kissing complex~$\RNKC$.
As an example of Theorem~\ref{thm:complexesCoincide}, let us now describe the corresponding non-crossing facets of~$\RNCC[\surface_{\bar Q}]$.

For a vertex~$v \in V$ on the boundary of~$\surface$, we denote by~$\vprevious{v}$ (resp.~$\vnext{v}$) the blossom vertex previous (resp.~next) to~$v$ when walking along  the boundary of~$\surface$ while keeping it on the right.
For an edge~$a$ of~$\dissection$, we denote by~$\vprevious{a}$ (resp.~$\vnext{a}$) the curve obtained by moving each endpoint~$v$ of~$a$ as follows:
\begin{itemize}
\item if~$v$ is on the boundary of~$\surface$, then move (continuously) $v$ along the boundary of~$\surface$ until it reaches~$\vprevious{v}$ (resp.~$\vnext{v}$),
\item if~$v$ is a puncture, then rotate around~$v$ in counterclockwise (resp.~clockwise) direction.
\end{itemize}
Examples are illustrated in \fref{fig:peakDeep}.
%
\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=.7]{peakDeep}}
	\caption{The curves~$\vprevious{a}$ (left) and $\vnext{a}$ (right) associated to an edge~$a$ of~$\dissection$ for three different dissections.}
	\label{fig:peakDeep}
\end{figure}

@@

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=1]{flip1}}
	\caption{A schematic representation of flips in the non-kissing complex. The flip exchanges the walk~$\omega = \rho \sigma \tau$ in the facet~$F$ (left) with the walk~$\omega' = \rho' \sigma \tau'$ in the facet~$F'$ (middle), using the walks~$\mu = \rho' \sigma \tau$ and~$\nu = \rho \sigma \tau'$. The walk~$\omega'$ kisses~$\omega$ but no other walk of~$F$ (right).}
	\label{fig:flip1}
\end{figure}

@@

\begin{proposition}
\label{prop:mutationAccordions}
Let~$F$ be a facet of the non-crossing complex~$\NCC$, and let~$\gamma \in F$.  We represent all curves on the universal cover of~$\surface(\bar Q)$.
Then~$F$ forms a~$B$-dissection of the surface, and~$\gamma$ lies in at least one of two configutations~$\ZZZ$ and~$\SSS$ with the other curves of the dissection (where the endpoints may go to infinity if punctures are involved). 
\begin{itemize}
\item Exactly one of the curves obtained by changing the~$\SSS$ to a~$\ZZZ$ and conversely by moving the endpoints of~$\gamma$ along the top and bottom curves is a~$\dissection$-accordion.
\item This~$\dissection$-accordion yields the flip or mutation of~$F$ at~$\gamma$.
\item If the flip is positive, then the~$\SSS$ is turned into a~$\ZZZ$.  If the flip is negative, then the~$\ZZZ$ is turned in to an~$\SSS$.
\end{itemize}
\end{proposition}

\begin{proof}
Let~$\omega = \walk(\gamma)$.  Using the notation of Proposition \ref{prop:flip}, the local configuration around~$\omega$ (as in Figure \ref{fig:flip1}) translates on the (universal cover of the) surface~$\surface(\bar Q)$ as follows.

\begin{figure}[h]
	\capstart
	\centerline{\includegraphics[scale=1]{flip2}}
	\caption{A schematic representation of flips in the non-crossing complex. The flip exchanges the curve~$\omega$ in the facet~$F$ (left) with the curve~$\omega'$ in the facet~$F'$ (middle), using the curves~$\mu$ and~$\nu$. The curve~$\omega'$ crosses~$\omega$ but no other curve of~$F$ (right).}
	\label{fig:flip2}
\end{figure}

@@

\begin{example}
\label{exm:gcdVectorsWalks}
For instance, the $\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of the facet illustrated in \fref{fig:gcdVectors} are given by
\[
\gvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	-1\!\! & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\cvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & \!\!-1 & \!\!\!\circled{1} \\
	0 & \!\!-1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\qquad\qquad
\dvectors{F} = 
\begin{blockarray}{ccc}
	{\color{blue} \bullet} & {\color{purple} \bullet} & \\[-.1cm]
	\begin{block}{[cc]c}
	1 & 0 & \!\!\!\circled{1} \\
	0 & -1 & \!\!\!\circled{2} \\
	\end{block}
\end{blockarray}
\]
(\ie columns are the $\b{g}$-, $\b{c}$-, $\b{d}$-vectors of the elements of the facet).

\begin{figure}[t]
	\capstart
	\centerline{\includegraphics[scale=.7]{gcdVectors}}
	\caption{A non-kissing facet of~$\RNKC$ (left), an accordion facet~$\RAC$ (middle) and a slalom facet~$\RSC$ (right) that correspond via the bijections of Theorem~\ref{thm:complexesCoincide} and Proposition~\ref{prop:accordionsSlaloms}. The~$\b{g}$-, $\b{c}$-, and $\b{d}$-matrices of this facet are given in Example~\ref{exm:gcdVectorsWalks}.}
	\label{fig:gcdVectors}
\end{figure}
\end{example}
